---
title: "LQ Analysis"
output: html_notebook
---

```{r}
library(ggmap)
library(ggplot2)
library(tmap)
library(sf)
library(lctools)
library(amap)
library(REAT)
library(dplyr)
firms <- read.csv("geocodedCombined.csv", stringsAsFactors = FALSE)
```

Categorize firms according to firm type
```{r}
firms_legal <- firms[grep("Legal", firms$type), ]
firms_consultancy <- firms[grep("Consultancy", firms$type), ]
firms_architectural <- firms[grep("Architectural", firms$type), ]
firms_bank <- firms[grep("Bank", firms$type), ]
firms_accountancy <- firms[grep("Accountancy", firms$type), ]
```

Delete entries with duplicate postal codes
```{r}
firms_legal <- firms_legal[!duplicated(firms_legal$postal_code),]
firms_consultancy <- firms_consultancy[!duplicated(firms_consultancy$postal_code),]
firms_architectural <- firms_architectural[!duplicated(firms_architectural$postal_code),]
firms_bank <- firms_bank[!duplicated(firms_bank$postal_code),]
firms_accountancy <- firms_accountancy[!duplicated(firms_accountancy$postal_code),]
firms <- firms[!duplicated(firms[,c("postal_code","type")]),]
```

------------------------------

#FOR LEGAL
Get legal companies in CBD
1. Find Singapore 01, 02, 03, 04, 05, and 06 in postal_code column
(CBD areas are postal codes that start with 01,02,03,04,05,06)
```{r}
legal_cbd <- firms_legal[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms_legal$postal_code), ]
```

Get legal companies in Jurong Lake District
```{r}
legal_jur <- firms_legal[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms_legal$postal_code), ]
```

Calculate no. of legal companies in CBD
```{r}
legal_cbd_count <- nrow(legal_cbd)
```

Calculate no. of legal companies in Jurong Lake District
```{r}
legal_jur_count <- nrow(legal_jur)
```

Get all companies in CBD
```{r}
all_cbd <- firms[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms$postal_code), ]
```

Get all companies in Jurong Lake District
```{r}
all_jur <- firms[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms$postal_code), ]
```

Calculate no. of companies in CBD
```{r}
all_cbd_count <- nrow(all_cbd)
```

Calculate no. of companies in Jurong Lake District
```{r}
all_jur_count <- nrow(all_jur)
```

Calculate no. of legal companies in country
```{r}
legal_country_count <- nrow(firms_legal)
```

Calculate no. of companies in country
```{r}
all_country_count <- nrow(firms)
```

Compute location quotient of legal firms in CBD
```{r}
locq(legal_cbd_count, all_cbd_count, legal_country_count, all_country_count)
```

Compute location quotient of legal firms in Jurong Lake District
```{r}
locq(legal_jur_count, all_jur_count, legal_country_count, all_country_count)
```

LQ Analysis:
If LQ < 1, The output is not sufficient to meet the local demand and imports are needed. It is also non-basic.

If LQ > 1 the output is more than sufficient to meet the local demand and exporting the surplus is an option. It is basic.

------------------------------

#FOR CONSULTANCY
Get consultancy companies in CBD
1. Find Singapore 01, 02, 03, 04, 05, and 06 in postal_code column
(CBD areas are postal codes that start with 01,02,03,04,05,06)
```{r}
consultancy_cbd <- firms_consultancy[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms_consultancy$postal_code), ]
```

Get consultancy companies in Jurong Lake District
```{r}
consultancy_jur <- firms_consultancy[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms_consultancy$postal_code), ]
```

Calculate no. of consultancy companies in CBD
```{r}
consultancy_cbd_count <- nrow(consultancy_cbd)
```

Calculate no. of consultancy companies in Jurong Lake District
```{r}
consultancy_jur_count <- nrow(consultancy_jur)
```

Get all companies in CBD
```{r}
all_cbd <- firms[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms$postal_code), ]
```

Get all companies in Jurong Lake District
```{r}
all_jur <- firms[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms$postal_code), ]
```

Calculate no. of companies in CBD
```{r}
all_cbd_count <- nrow(all_cbd)
```

Calculate no. of companies in Jurong Lake District
```{r}
all_jur_count <- nrow(all_jur)
```

Calculate no. of consultancy companies in country
```{r}
consultancy_country_count <- nrow(firms_consultancy)
```

Calculate no. of companies in country
```{r}
all_country_count <- nrow(firms)
```

Compute location quotient of consultancy firms in CBD
```{r}
locq(consultancy_cbd_count, all_cbd_count, consultancy_country_count, all_country_count)
```

Compute location quotient of consultancy firms in Jurong Lake District
```{r}
locq(consultancy_jur_count, all_jur_count, consultancy_country_count, all_country_count)
```

LQ Analysis:
If LQ < 1, The output is not sufficient to meet the local demand and imports are needed. It is also non-basic.

If LQ > 1 the output is more than sufficient to meet the local demand and exporting the surplus is an option. It is basic.

------------------------------

#FOR ARCHITECTURAL
Get architectural companies in CBD
1. Find Singapore 01, 02, 03, 04, 05, and 06 in postal_code column
(CBD areas are postal codes that start with 01,02,03,04,05,06)
```{r}
architectural_cbd <- firms_architectural[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms_architectural$postal_code), ]
```

Get architectural companies in Jurong Lake District
```{r}
architectural_jur <- firms_architectural[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms_architectural$postal_code), ]
```

Calculate no. of architectural companies in CBD
```{r}
architectural_cbd_count <- nrow(architectural_cbd)
```

Calculate no. of architectural companies in Jurong Lake District
```{r}
architectural_jur_count <- nrow(architectural_jur)
```

Get all companies in CBD
```{r}
all_cbd <- firms[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms$postal_code), ]
```

Get all companies in Jurong Lake District
```{r}
all_jur <- firms[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms$postal_code), ]
```

Calculate no. of companies in CBD
```{r}
all_cbd_count <- nrow(all_cbd)
```

Calculate no. of companies in Jurong Lake District
```{r}
all_jur_count <- nrow(all_jur)
```

Calculate no. of architectural companies in country
```{r}
architectural_country_count <- nrow(firms_architectural)
```

Calculate no. of companies in country
```{r}
all_country_count <- nrow(firms)
```

Compute location quotient of architectural firms in CBD
```{r}
locq(architectural_cbd_count, all_cbd_count, architectural_country_count, all_country_count)
```

Compute location quotient of architectural firms in Jurong Lake District
```{r}
locq(architectural_jur_count, all_jur_count, architectural_country_count, all_country_count)
```

LQ Analysis:
If LQ < 1, The output is not sufficient to meet the local demand and imports are needed. It is also non-basic.

If LQ > 1 the output is more than sufficient to meet the local demand and exporting the surplus is an option. It is basic.

------------------------------

#FOR BANK
Get bank firms in CBD
1. Find Singapore 01, 02, 03, 04, 05, and 06 in postal_code column
(CBD areas are postal codes that start with 01,02,03,04,05,06)
```{r}
bank_cbd <- firms_bank[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms_bank$postal_code), ]
```

Get bank firms in Jurong Lake District
```{r}
bank_jur <- firms_bank[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms_bank$postal_code), ]
```

Calculate no. of bank firms in CBD
```{r}
bank_cbd_count <- nrow(bank_cbd)
```

Calculate no. of bank firms in Jurong Lake District
```{r}
bank_jur_count <- nrow(bank_jur)
```

Get all companies in CBD
```{r}
all_cbd <- firms[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms$postal_code), ]
```

Get all companies in Jurong Lake District
```{r}
all_jur <- firms[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms$postal_code), ]
```

Calculate no. of companies in CBD
```{r}
all_cbd_count <- nrow(all_cbd)
```

Calculate no. of companies in Jurong Lake District
```{r}
all_jur_count <- nrow(all_jur)
```

Calculate no. of bank firms in country
```{r}
bank_country_count <- nrow(firms_bank)
```

Calculate no. of companies in country
```{r}
all_country_count <- nrow(firms)
```

Compute location quotient of bank firms in CBD
```{r}
locq(bank_cbd_count, all_cbd_count, bank_country_count, all_country_count)
```

Compute location quotient of architectural firms in Jurong Lake District
```{r}
locq(bank_jur_count, all_jur_count, bank_country_count, all_country_count)
```

LQ Analysis:
If LQ < 1, The output is not sufficient to meet the local demand and imports are needed. It is also non-basic.

If LQ > 1 the output is more than sufficient to meet the local demand and exporting the surplus is an option. It is basic.

------------------------------

#FOR ACCOUNTANCY
Get accountancy firms in CBD
1. Find Singapore 01, 02, 03, 04, 05, and 06 in postal_code column
(CBD areas are postal codes that start with 01,02,03,04,05,06)
```{r}
accountancy_cbd <- firms_accountancy[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms_accountancy$postal_code), ]
```

Get accountancy firms in Jurong Lake District
```{r}
accountancy_jur <- firms_accountancy[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002", firms_accountancy$postal_code), ]
```

Calculate no. of accountancy firms in CBD
```{r}
accountancy_cbd_count <- nrow(accountancy_cbd)
```

Calculate no. of architectural companies in Jurong Lake District
```{r}
accountancy_jur_count <- nrow(accountancy_jur)
```

Get all companies in CBD
```{r}
all_cbd <- firms[grep("Singapore 01|Singapore 02|Singapore 03|Singapore 04|Singapore 05|Singapore 06|Singapore 07|Singapore 08|Singapore 14|Singapore 15|Singapore 16|Singapore 09|Singapore 10|Singapore 11|Singapore 120|Singapore 13|Singapore 17|Singapore 18|Singapore 19|Singapore 20|Singapore 21|Singapore 22|Singapore 23|Singapore 24|Singapore 25|Singapore 26|Singapore 27|Singapore 28|Singapore 29|Singapore 30|Singapore 31|Singapore 32|Singapore 33|Singapore 34|Singapore 35|Singapore 36|Singapore 37|Singapore 38|Singapore 39|Singapore 40|Singapore 41|Singapore 42|Singapore 43|Singapore 44|Singapore 45|Singapore 57|Singapore 58|Singapore 59|Singapore 77", firms$postal_code), ]
```

Get all companies in Jurong Lake District
```{r}
all_jur <- firms[grep("Singapore 608|Singapore 609|Singapore 6001|Singapore 6002|Singapore 6002", firms$postal_code), ]
```

Calculate no. of companies in CBD
```{r}
all_cbd_count <- nrow(all_cbd)
```

Calculate no. of companies in Jurong Lake District
```{r}
all_jur_count <- nrow(all_jur)
```

Calculate no. of accountancy firms in country
```{r}
accountancy_country_count <- nrow(firms_accountancy)
```

Calculate no. of companies in country
```{r}
all_country_count <- nrow(firms)
```

Compute location quotient of accountancy firms in CBD
```{r}
locq(accountancy_cbd_count, all_cbd_count, accountancy_country_count, all_country_count)
```

Compute location quotient of architectural firms in Jurong Lake District
```{r}
locq(accountancy_jur_count, all_jur_count, accountancy_country_count, all_country_count)
```

LQ Analysis:
If LQ < 1, The output is not sufficient to meet the local demand and imports are needed. It is also non-basic.

If LQ > 1 the output is more than sufficient to meet the local demand and exporting the surplus is an option. It is basic.